---
title: "testimomials"
author: "Sumit Kant"
date: "21 May 2017"
output: html_document
---

## Load data

Extracting only the student IDs
```{r warning=FALSE}
testimonials <- read.csv("testimonials.csv")
ids <- testimonials[,c(1,4)]
head(ids)
```

## Subsetting Data

At IIM Lucknow, there are primarily two programs, Post Graduate Diploma in Management (PGDM) and Agri-Business Management (ABM). Since ABM is a small group.We will look into their network, for the sake of simpliity

```{r}
abm.ids <- ids[grep("abm", ids$PGP.ID),]
head(abm.ids)
dim(abm.ids)
```

```{r}
unique(abm.ids$PGP.ID)
```

So there are 20 students in ABM Program. Let's look at their social network.

```{r message=FALSE}
# Loading libraries
library(ggplot2)
library(ggnet)
library(GGally)
library(network)
library(RColorBrewer)
```

```{r}
net <- network(abm.ids[,c(2,1)], directed = TRUE)

x = data.frame(frndcrcl = network.vertex.names(net))
x <- abm.ids$PGP.ID
net %v% "frndcrcl" = as.character(x)
```

## Making Color Palette

```{r}
getPalette = colorRampPalette(brewer.pal(9, "Set1"))
colors <- getPalette(length(unique(abm.ids$PGP.ID)))
names(colors) <- unique(abm.ids$PGP.ID)
```

# Plotting the net
```{r}
ggnet2(net, mode = "fruchtermanreingold",
       alpha = 0.85, 
       size = 10, 
       edge.alpha = 0.35,
       edge.color = "gray50",
       label = abm.ids$PGP.ID,
       label.size = 4,
       color = "frndcrcl",
       palette = colors,
       arrow.type = "closed", arrow.size = 8, arrow.gap = 0.02, legend.position = "none")
```

# Let's look at PGP group

```{r}
pgp.ids <- ids[grep("pgp", ids$PGP.ID),]
head(pgp.ids)
dim(pgp.ids)
```

```{r}
length(unique(pgp.ids$PGP.ID))
```

So there are a lot of students in PGP programme as you see.

```{r}
net.pgp <- network(pgp.ids[,c(2,1)], directed = TRUE)

y = data.frame(frndcrcl = network.vertex.names(net.pgp))
y <- pgp.ids$PGP.ID
net.pgp %v% "frndcrcl" = as.character(y)
```

## Making Color Palette

```{r}
getPalette = colorRampPalette(brewer.pal(9, "Set1"))
colors.pgp <- getPalette(length(unique(pgp.ids$PGP.ID)))
names(colors.pgp) <- unique(pgp.ids$PGP.ID)
head(colors.pgp)
```

# Plotting the net
```{r}
ggnet2(net.pgp, mode = "fruchtermanreingold",
       alpha = 0.85, 
       size = 6, 
       edge.alpha = 0.35,
       edge.color = "gray50",
       label = pgp.ids$PGP.ID,
       label.size = 3,
       color = "frndcrcl",
       palette = colors.pgp,
       arrow.type = "closed", arrow.size = 6, arrow.gap = 0.02, legend.position = "none")
```

